Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
(invar)

Analyzing this loop using widening and narrowing on convex polyhedra or octagons yields the loop invariant $0 \leq x \leq 51 \land y = x$. Now, the transition at line~5 becomes feasible; and we analyze the full loop, starting iterations from $0 \leq x \leq 51 \land y = x$, and obtain invariant~\ref{eqn:triangle}.

>>>>

Analyzing this loop using widening and narrowing on convex polyhedra or octagons yields the loop invariant $0 \leq x \leq 51 \land y = x$. Now, the transition at line~5 becomes feasible; and we analyze the full loop, starting iterations from $0 \leq x \leq 51 \land y = x$, and obtain invariant~(\ref{eqn:triangle}).
